Novelty Detection for Semantic Place Categorization

### 2011-07-14 thesis/presentation.tex
More updates to presentation.
Probably not final state yet, but I am running out of time.

\subsection{Conceptual Map}
\begin{frame}{Conceptual Map}
  \begin{columns}[c]
  \column{0.5\textwidth}
    \begin{figure}
      \includegraphics[width=\textwidth]{figures/chaingraph.pdf}
    \end{figure}
  \column{0.5\textwidth}
    \begin{itemize}
      \item Uncertain Ontology
      \item Probabilistic Inference
      \item Use of Graphical Models
    \end{itemize}
  \end{columns}

@@

\begin{frame}{Probabilistic Graphical Models}
Provides us methods to relate and combine the several information,
Can be approximated, handle uncertainties, etc\dots

@@

@@

\subsection{Summary}
\begin{frame}{Summary}
\begin{itemize}
\item Studies a semantic mapping process
\item Studies novelty detection
\item Proposes a method to perform detection of novel categories
      of a variable when the graph structure is dynamic.
\end{itemize}
\end{frame}

>>>>

\subsection{Conceptual Map}
\begin{frame}{Conceptual Map}
  \begin{columns}[c]
  \column{0.5\textwidth}
    \begin{figure}
      \includegraphics[width=\textwidth]{figures/chaingraph.pdf}
    \end{figure}
  \column{0.5\textwidth}
    \begin{block}{Conceptual Map}
      The ontology is used to identify instances of the concepts and categories
      And perform probabilistic semantic mapping using graphical models.
    \end{block}
  \end{columns}

@@

\begin{frame}{Probabilistic Graphical Models}
Provides us methods to relate and combine the several variables in a probabilistic way.
Allowing to deal with uncertain information and infer variable states.

\vfill

@@

\begin{frame}{Results - Variable Graph Size}

\begin{columns}[c]
  \column{0.5\textwidth}
  \centering
  \includegraphics[width=0.8\textwidth]{results/synthetic-3features.pdf} \\ 3 sensed features
  \column{0.5\textwidth}
  \centering
  \includegraphics[width=0.8\textwidth]{results/synthetic-5features.pdf} \\ 5 sensed features
\end{columns}
\begin{columns}[c]
  \column{0.5\textwidth}
  \centering
  \includegraphics[width=0.8\textwidth]{results/synthetic-10features.pdf} \\ 10 sensed features
  \column{0.5\textwidth}
  \centering
  \includegraphics[width=0.8\textwidth]{results/synthetic-50features.pdf} \\ 50 sensed features
\end{columns}
\end{frame}

@@

\subsection{Summary}
\begin{frame}{Summary}
\begin{itemize}
\item Studies a semantic mapping process
\item Studies novelty detection
\item Proposes a method to perform detection of novel categories
      of a variable when the graph structure is dynamic.
\item Shows access to unlabelled data can greatly increase performance.
\end{itemize}
\end{frame}
